The effect of symbols in government communications on citizens' trust, and its interaction with substantive information

### 2018-06-15 paper2_information and symbols.Rmd
Add files via upload

---
title: "The effect of symbols in government communications on citizens' trust, and its interaction with substantive information"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

@@

Preliminary draft (last edited at `r Sys.Date()`)[^footnote_scripts] - do not cite without author's permission.

@@

*Effective public communications have been proposed as a remedy for citizens' distrust in government. The studies that explored the effectiveness of government communications have focused mainly on the extent to which they provide substantive information about bureaucracies' performance and policies. Recently, a few studies pointed to the effect of symbolic elements, entangled in these communications (e.g. logos, images and celebrities). Still, we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information. Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements can increase citizens' trust via two mechanisms: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication. Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust. I examine these hypotheses via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans. The results confirm that symbolic elements in communications increase citizens' trust. The effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to scrutinize their content. I discuss the implications of these findings for democratic responsiveness and accountability.*

@@

In addition to information manipulation, the participants are randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment (real symbols), control no symbols and control fake symbols. In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement". Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy; Friedman's image from the "starting to think green" campaign was attached to the air-pollution policy. In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images. Finally, in the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people. The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design. Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.[^footnote_symbols_manipulation_checks] In that sense, it can be regarded as a placebo. The symbols conditions are displayed in **Appendix B**. That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e. one strong and one weak), enables me later to analyze the interaction between these two manipulations both via between- and within-subjects.

@@

@@

According to my first hypothesis, I expect that the real symbols condition will have a positive main effect on subjects' trust in the policy plans. According to my second hypothesis, I expect a positive interaction between the real symbols and weak policy plan. Namely, the effect of the real symbols is expected to be greater among those subjects who were assigned to the weak policy. In **Table 1**, I test these two hypotheses via regression analyses. To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level via `lme4` R package.[^footnote_icc] In Model 1 I regress trust in policy on the symbols manipulation. Thereafter, in Models 2 and 3, I add the information manipulation, and the interaction between them. In these models, I the reference category for the symbols manipulation is the no-symbols condition.

[^footnote_icc]: ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`.

@@

In Model 1.2, the effect of the symbols remains intact, and the effect of the weak policy condition is negative and significant (*Coef* = `r mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]). In Model 1.3, the interaction between weak policy and real symbols is positive and significant, whereas the interaction with the fake symbols is insignificant. The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively). When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1). Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100)%>%round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]). The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05). To facilitate the interpretation of this interaction, **Figure 6** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.

**Figure 6: The effect of symbolic elements on trust under weak vs. strong information**

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=6,fig.height=4}
ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(INFORMATION_n)))+ 
  theme_classic()+
  #geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.2,size=0.5,position=position_dodge(0.1),color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = INFORMATION_n,linetype=INFORMATION_n),position=position_dodge(0.1))+
  scale_shape_manual(guide=F,values=c(19,1))+
  scale_linetype_manual(name="Information",values=c(1,4),labels=c("Weak policy","Strong policy"))+
  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
```

@@

The interaction between between symbols can be also tested *within-subjects*, by comparing the averaged delta across the different symbols conditions. Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition. This comparison is graphically displayed in **Figure 6**. The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2]%>%round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2]%>%round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]%>%round(3)` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]%>%round(3)`, respectively). The differences between the two control groups are insignificant. These results further support my above finding that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.

**Figure 6: The effect of symbolic elements on within-subject delta between strong and weak policies**

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=4,fig.height=4}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), WITHIN_DELTA))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,color="#9999CC",alpha=0.7) + 
  stat_summary(fun.y = mean, geom = "point", size=2)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="Symbolic elements",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Within subject delta", breaks = seq(0,1,by=0.1))

@@

@@

In all four models, the coefficients of the real symbols are negative and significant, and the coefficients of the fake symbols are insignificant. The real symbols decreased the number of second subjects spent on the pages of the policy plans in the online survey, compared with both control groups.[^footnote_RT_symbols] The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), yet it is not sufficiently significant compared with the fake symbols. The averaged memory score of subjects who saw the real symbols was significantly lower, compared with both the no logo and the fake logo groups (*Coef* = `r mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`], and `r mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`], respectively).[^footnote_memory_symbols] There is no significant change to the results when adding the the effects of the information manipulation (in Models 2.2, 2.4). The coefficients of the weak policy in these models suggest that those who saw the fictitious, weak policy plans, spent more time on their pages, yet were less likely to state items that were included in them. **Figure 7** graphically displays the descriptive comparison of the elaboration measures across the symbols conditions. The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.

@@

**Figure 7: The effect of symbolic elements on elaboration**

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold',, fig.width=4,fig.height=4}
ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), ELABORATION_time_log))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,color="#9999CC",alpha=0.7) + 
  stat_summary(fun.y = mean, geom = "point", size=1.5)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
  scale_y_continuous(name = "Reaction Time (log)")

ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), MEMORY_score))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,color="#9999CC",alpha=0.7) + 
  stat_summary(fun.y = mean, geom = "point", size=1.5)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
  scale_y_continuous(name = "Memory score")
```

>>>>

---
title: "The effect of symbols in government communications on citizens' trust, and its interaction with substantive information"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  word_document: default
  pdf_document:
    toc: yes
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

@@

Last edited at `r Sys.Date()`)[^footnote_scripts].

@@

*Effective public communications have been proposed as a remedy for citizens' distrust in government. The studies that explored the effectiveness of government communications have focused mainly on the extent to which they provide substantive information about bureaucracies' performance and policies. Recently, a few studies pointed to the effect of symbolic elements, entangled in these communications (e.g. logos, images and celebrities). Still, we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information. Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements can increase citizens' trust via two mechanisms: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication. Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust. I examine these expectations via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans. The results confirm that symbolic elements in communications increase citizens' trust. The effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to scrutinize their content. I discuss the implications of these findings for democratic responsiveness and accountability.*

@@

In addition to information manipulation, the participants are randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment (real symbols), control no symbols and control fake symbols. In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement". Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy; Friedman's image from the "starting to think green" campaign was attached to the air-pollution policy. In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images. Finally, in the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people. The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design. Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.[^footnote_symbols_manipulation_checks] In that sense, it can be regarded as a placebo. The symbols conditions are displayed in **Appendix B**. Further details about the images in the real and fake symbols conditions are found in the supplementary appendix. That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e. one strong and one weak), enables me later to analyze the interaction between these two manipulations both via between- and within-subjects.

@@

In addition to the above independent variables, the survey also included control items regarding respondents’ age, gender, education, income, home ownership, age of their children, political ideology, trust in governemnt, interest in environmental issues and residence in the Haifa-Bay area. Summary statistics for all our variables are available in the supplementary appendix.

@@

According to my first hypothesis, I expect that the real symbols condition will have a positive main effect on subjects' trust in the policy plans. According to my second hypothesis, I expect a positive interaction between the real symbols and weak policy plan. Namely, the effect of the real symbols is expected to be greater among those subjects who were assigned to the weak policy. In **Table 1**, I test these two hypotheses via regression analyses. To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level via `lme4` R package (ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`). In Model 1 I regress trust in policy on the symbols manipulation. Thereafter, in Models 2 and 3, I add the information manipulation, and the interaction between them. In these models, I the reference category for the symbols manipulation is the no-symbols condition.

@@

In Model 1.2, the effect of the symbols remains intact, and the effect of the weak policy condition is negative and significant (*Coef* = `r mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]). In Model 1.3, the interaction between weak policy and real symbols is positive and significant, whereas the interaction with the fake symbols is insignificant. The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively). When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1). Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100)%>%round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]). The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05). To facilitate the interpretation of this interaction, **Figure 4** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.

**Figure 4: The effect of symbolic elements on trust under weak vs. strong information**

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=6,fig.height=4}
ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(INFORMATION_n)))+ 
  theme_classic()+
  #geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.65),
               width=0.2,size=0.5,position=position_dodge(0.1),color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = INFORMATION_n,linetype=INFORMATION_n),position=position_dodge(0.1))+
  scale_shape_manual(guide=F,values=c(19,1))+
  scale_linetype_manual(name="Information",values=c(1,4),labels=c("Weak policy","Strong policy"))+
  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
```

*Note*: Error bars represent 90% confidence intervals.

@@

The interaction between between symbols can be also tested *within-subjects*, by comparing the averaged delta across the different symbols conditions. Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition. This comparison is graphically displayed in **Figure 5**. The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2]%>%round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2]%>%round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]%>%round(3)` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]%>%round(3)`, respectively). The differences between the two control groups are insignificant. These results further support my above finding that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.

**Figure 5: The effect of symbolic elements on within-subject delta between strong and weak policies**

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=4,fig.height=4}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), WITHIN_DELTA))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
                              fun.args = list(mult = 1.65),
                              width=0.1,size=0.5,color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=2)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="Symbolic elements",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Within subject delta", breaks = seq(0,1,by=0.1))

@@

*Note*: Error bars represent 90% confidence intervals.

@@

In all four models, the coefficients of the real symbols are negative and significant, and the coefficients of the fake symbols are insignificant. The real symbols decreased the number of second subjects spent on the pages of the policy plans in the online survey, compared with both control groups.[^footnote_RT_symbols] The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), yet it is not sufficiently significant compared with the fake symbols. The averaged memory score of subjects who saw the real symbols was significantly lower, compared with both the no logo and the fake logo groups (*Coef* = `r mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`], and `r mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`], respectively).[^footnote_memory_symbols] There is no significant change to the results when adding the the effects of the information manipulation (in Models 2.2, 2.4). The coefficients of the weak policy in these models suggest that those who saw the fictitious, weak policy plans, spent more time on their pages, yet were less likely to state items that were included in them. **Figure 6** graphically displays the descriptive comparison of the elaboration measures across the symbols conditions. The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.

@@

**Figure 6: The effect of symbolic elements on elaboration**

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold',, fig.width=4,fig.height=4}
ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), ELABORATION_time_log))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
                              fun.args = list(mult = 1.65),
                              width=0.1,size=0.5,color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.5)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
  scale_y_continuous(name = "Reaction Time (log)")

ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), MEMORY_score))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
                              fun.args = list(mult = 1.65),
                              width=0.1,size=0.5,color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.5)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
  scale_y_continuous(name = "Memory score")
```

*Note*: Error bars represent 90% confidence intervals.
